The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-10-10 paper.tex
re-order some sections of the paper
almost a final draft...

Current 21~cm cosmology experiments can be broadly separated into two classes: global experiments
that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm transition
after averaging over the entire sky (otherwise known as the monopole), and power spectrum
experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
\citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
\citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
\citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
\citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}.

@@

The structure of this paper is as follows. In \S\ref{sec:imaging}, we present Tikhonov-regularized
$m$-mode analysis imaging, a new imaging technique that allows us to image the entire visible sky in
one coherent synthesis imaging step with exact widefield corrections. In \S\ref{sec:observations} we
describe our observations with the Owens Valley Long Wavelength Array (OVRO-LWA). In
\S\ref{sec:results} we present the sky maps, and in \S\ref{sec:error} we discuss some of the sources
of error present in the maps. Finally in \S\ref{sec:compare} the new sky maps are compared against
other low-frequency sky maps, and in \S\ref{sec:conclusion} we present our conclusions.

@@

Another way of looking at the problem is that because the interferometer is not sensitive to part of
the southern hemisphere, there are infinitely many possible solutions to
Equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well.  We will
regularize the problem and apply an additional constraint that prefers a unique yet physically
reasonable solution.

@@

While Tikhonov regularization will force unmeasured modes to zero, if a prior map of the sky already
exists, it would be preferrable to instead minimize $\|\b v - \b B\b a\|^2 + \varepsilon \|\b a-\b
a_\text{prior}\|^2$.

@@

\subsubsection{The Moore-Penrose Pseudoinverse}

The Moore-Penrose pseudoinverse (denoted in this paper with a superscript $\dagger$), is commonly
applied to find the minimum-norm linear-least squares solution to a set of linear equations. This
can be used in place of Tikhonov regularization as
\begin{equation}
    \b{\hat a}_\text{Moore-Penrose} = \b B^\dagger\b v\,.
\end{equation}
Much like Tikhonov regularization, the Moore-Penrose pseudoinverse sets components with small
singular values (below some user-defined threshold) to zero. Components with large singular values
(above the user-defined threshold) are included in the calculation at their full amplitude with no
down-weighting of modes near the threshold. The essential difference between using the Moore-Penrose
pseudoinverse and Tikhonov regularization is that the pseudoinverse defines a hard transition from
on to off. Modes are either set to zero or included in the map at their full amplitude. On the other
hand Tikhonov regularization smoothly interpolates between these behaviors. Because of this,
Tikhonov regularization tends to produce better results in practical applications.

@@

In compressed-sensing applications, the $L^1$-norm is used in place of the $L^2$-norm in order to
encourage sparsity in the reconstructed signal. By expressing the sky in terms of spherical
harmonics there is no such expectation of sparsity in the solution, and so the $L^1$-norm is
inappropriate for this application.

Wiener filtering can also be used in place of Tikhonov regularization in the event that the observer
has a prior expectation on the covariance of the spherical harmonic coefficients in order to
interpolate missing information. This technique is demonstrated for simulated measurements by
\citet{2016arXiv161203255B}.

In this work we elect to pursue Tikhonv regularization due to its computational simplicity, smooth
down-weighting of noisy modes, and independence of prior information.

@@

We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A,
Per~B\footnote{
    At 74~MHz, Per~B is about two times brighter than Per~A.
}, and
3C~353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, and $Z_8^8$) and the beam amplitude
at zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
model at several frequencies. This process is repeated for each frequency channel.

@@

Small scale fluctuations are best characterized by source scintillation and refractive offsets.
Figure~\ref{fig:scintillation} shows the apparent flux and position offset of Cyg~A and Cas~A as a
function of time over the entire observing period. Both sources exhibit rapid scintillation on the
timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
A to have a measured flux variations of 50\% between adjacent 13 second integrations.  The variance
at 36.528~MHz compared with the variance at 73.152~MHz is consistent with an ionospheric $\nu^{-2}$
origin. The measured position offset of each source is a measurement of the ionospheric phase
gradient across the array.  This varies on slower 10 minute timescales refracting each source by as
much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves in the ionosphere
pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K} observe $\sim
1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the day on similar
$\sim10$ minute timescales.  The impact of these effects on the sky maps is simulated in
\S\ref{sec:ionosphere}.

@@

In order to account for propagation effects through the ionosphere direction-dependent calibration
and peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S} must be used.  Direction-dependent
calibration allows the per-antenna amplitude and phase towards a bright astronomical source to be
free parameters. In the dataset used in this paper, scintillation and refractive-offset events on
the timescale of a single integration (13 seconds) are observed (Figure~\ref{fig:scintillation}).
Therefore the direction dependent calibration changes on these timescales and we must solve for one
set of complex gains per source per integration.

@@

Other bright sources namely Vir~A, Tau~A, Her~A, Hya~A, Per~B, and 3C~353 are also removed from
the visibilities prior to imaging. Because these sources are much fainter than Cyg~A and Cas~A, we
do not need resolved source models to be able to remove these sources from the visibilities without
residual sidelobes contaminating the image.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/spectral-index/ovro-lwa-sky-map.pdf}
    \caption{
        This Mollweide-projected map is constructed from 3 maps of the sky at 36.528~MHz (red),
        52.224~MHz (green), and 73.152~MHz (blue). The maps are scaled by $\nu^{2.5}$ before
        combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}).
        Therefore regions with a spectral index of $-2.5$ appear white. Areas with a steeper index
        appear red and areas with a flatter spectral index appear blue.
    }
    \label{fig:three-color}
\end{figure*}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/spectral-index/better-internal-spectral-index}
    \caption{
        \todo{updated this caption}
        This plot shows the local spectral index (estimated by means of a local T-T plot) as a
        contour plot. The contours are overlaid on the three-color image from
        Figure~\ref{fig:three-color}. The spectral index fit along the galactic plane is masked
        because T-T plots assume a single emission mechanism operates in a given region. Along the
        galactic plane free-free dominated regions lie in close proximity to synchrotron dominated
        regions. This introduces large systematic errors to the power-law fit unless care is taken
        to cleanly separate the two types of emission mechanisms.
    }
    \label{fig:internal-spectral-index}
\end{figure*}

@@

Due to the considerations presented by \citet{2016ApJ...826..116V}, each of these maps is monopole
subtracted ($a_{00}=0$). Consequently a simple pixel-by-pixel powerlaw fit will be unduly affected
by the choice of zero-level correction. Instead, temperature-temperature plots (T-T plot) can be
used to measure the spectral index independently of any zero-level corrections
\citep{1962MNRAS.124..297T}. This method relies on the assumption that all pixels in a given region
are described by the same power law. In Figure~\ref{fig:internal-spectral-index} the spectral index
is locally estimated within a region $\sim10^\circ$ across by constructing a local T-T plot at every
pixel between the maps at 36.528~MHz and 73.152~MHz. The spectral index contours are overlaid on the
3-color image from Figure~\ref{fig:three-color} where free-free regions responsible for flattening
the spectral index in the galactic plane are plainly visible as extended blue blobs.  Similarly the
spectral index can be seen to steepen as galactic latitude increases (this is a transition from blue
to white to yellow that is also evident in the spectral index contours).

In order to suppress sources of terrestrial interference, all spherical harmonics with $m=0$, or
$m=1$ and $l>100$ are filtered from the map (where the spherical harmonics are defined in the J2017
coordinate system). As will be discussed in \S\ref{sec:rfi}, these spherical harmonics are
particularly susceptible to contamination by RFI and common-mode pickup. As a consequence,
astronomical emission that circles the J2017 north celestial pole (NCP) is filtered from the maps.
This filtering creates negative rings around the NCP at the declination of bright point sources.
These rings are naturally removed from the map during CLEANing as long as this filtering step is
including in the PSF calculation.

The noise in each map is empirically measured using jackknife resampling. The dataset is split into
even- and odd-numbered integrations. These two groups are imaged and cleaned independently, before
being compared against the maps constructed from all of the available data using the standard
jackknife variance estimator. This estimate of the variance includes all sources of error that
operate on $\sim13$ second timescales (the integration time) such as thermal noise in rapid
ionospheric fluctuations, but does not account for more slowly varying effects (for example,
sidereal variation in the system temperature or day-night fluctuations in the ionosphere). These
noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
noise $<900$ mJy and therefore each map is likely at or near the confusion limit.

Each map from Figure~\ref{fig:channel-maps} is freely available online in Healpix format
\citep{2005ApJ...622..759G} on LAMBDA (\url{https://lambda.gsfc.nasa.gov/}).

@@

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/postage-stamps/3C134}
    \caption{
        A zoom-in of 3C~134 at 36.528~MHz (left panel), 52.224~MHz (middle panel), and 73.152~MHz
        (right panel). At 36.528~MHz there are $\sim10\%$ artifacts around 3C~134 that persist after
        CLEANing due to ionospheric effects. As expected for an ionospheric origin, these artifacts
        decrease in amplitude as frequency increases.
    }
    \label{fig:3C134}
\end{figure*}

The maps presented in Figure~\ref{fig:channel-maps} do not account for any off-diagonal terms
arising from ionospheric fluctuations. The effect of this can be seen in
Figure~\ref{fig:ionospheric-simulations}. In this simulation at 36.528~MHz, a point source is placed
at the location of Cas A. In the first panel the source flux traces the beam model exactly and the
source is always located exactly at the location of Cas A. In the middle panel, the source is
allowed to scintillate in the same way Cas A does in Figure~\ref{fig:scintillation}. The image of
the point source is effectively unchanged from the ideal PSF. In the right panel, the source
position is allowed to vary in the same way Cas A does in Figure~\ref{fig:scintillation}. The
refractive offsets lead to a clear degradation of the sidelobes. Because the sidelobes are altered
from that of the ideal PSF, refractive offsets will restrict the dynamic range it is possible to
obtain with the CLEAN algorithm described in \S\ref{sec:clean}. This effect can be clearly seen in
Figure~\ref{fig:3c134}, where 10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As
expected for an ionospheric effect these errors decrease to a few percent at 52.224~MHz, and less at
73.152~MHz. We therefore conclude that ionospheric effects directly limit the dynamic range in the
vicinity of bright point sources.

The second case is more subtle. Sources are observed at a wide range of locations in the primary
beam of the antenna. The imaging process must reconcile all of these observations together, and the
beam model provides the instructions for how to do this. In the event of an error in the beam model,
it can be expected that the beam will introduce errors into the sky maps that will limit the dynamic
range in the vicinity of bright point sources.  \citet{2015PhRvD..91h3514S} simulate the effect of
beam errors on a cosmological analysis concluding that the beam must be known to one part in $10^4$.
Our requirements are significantly less stringent because we are estimating the sky brightness
instead of estimating the amplitude of a faint cosmological signal in the presence of foreground
emission that dominates the signal by 5 orders of magnitude. In fact in \S\ref{sec:ionopshere} we
found that ionospheric effects likely dominate over other sources of error that affect the PSF
shape. Therefore we conclude that the beam models generated in \S\ref{sec:beam} are sufficient to
limit the effect of beam errors on the PSF to at least less than those introduced by the ionosphere.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparisons with Other Sky Maps}\label{sec:compare}

\subsection{Guzm\'{a}n 45 MHz Map}

>>>>

Current 21~cm cosmology experiments can be broadly separated into two classes: global experiments
that are aiming to detect the spectral signature of the cosmologically redshifted 21~cm transition
after averaging over the entire sky (otherwise known as the monopole), and power spectrum
experiments that incorporate angular information to attempt to measure the 3D spatial power spectrum
of cosmological 21~cm perturbations.  Ongoing global experiments include EDGES
\citep{2010Natur.468..796B, 2017ApJ...847...64M}, LEDA \citep{2017arXiv170909313P}, BIGHORNS
\citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V}, and SARAS 2
\citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
\citep{2016ApJ...833..102B, 2016MNRAS.460.4320E}.

@@

The structure of this paper is as follows. In \S\ref{sec:imaging}, we present Tikhonov-regularized
$m$-mode analysis imaging, a new imaging technique that allows us to image the entire visible sky in
one coherent synthesis imaging step with exact widefield corrections. In \S\ref{sec:observations} we
describe our observations with the Owens Valley Long Wavelength Array (OVRO-LWA). In
\S\ref{sec:results} we present the sky maps and compare these maps against other low-frequency sky
maps.  In \S\ref{sec:error} we discuss some of the sources of error present in the maps, and finally
in \S\ref{sec:conclusion} we present our conclusions.

@@

Another way of looking at the problem is that because the interferometer is not sensitive to part of
the southern hemisphere, there are infinitely many possible solutions to
Equation~\ref{eq:m-mode-matrix-equation} that will fit the measured data equally well.  We will
therefore regularize the problem and apply an additional constraint that prefers a unique yet
physically reasonable solution.

@@

@@

@@

The choice of applying Tikhonov regularization to $m$-mode analysis imaging is not unique. There
exists a plethora of alternative regularization schemes that could also be applied. Each
regularization scheme has its own advantages and disadvantages. For instance Tikhonov regularization
is simple, independent of prior information, and sets unmeasured modes to zero (a sensible
expectation). We will now briefly discuss a few other alternatives.

The Moore-Penrose pseudoinverse (denoted with a superscript $\dagger$), is commonly applied to find
the minimum-norm linear-least squares solution to a set of linear equations. This can be used in
place of Tikhonov regularization as
\begin{equation}
    \b{\hat a}_\text{Moore-Penrose} = \b B^\dagger\b v\,.
\end{equation}
Much like Tikhonov regularization, the Moore-Penrose pseudoinverse sets components with small
singular values (below some user-defined threshold) to zero. Components with large singular values
(above the user-defined threshold) are included in the calculation at their full amplitude with no
down-weighting of modes near the threshold. The essential difference between using the Moore-Penrose
pseudoinverse and Tikhonov regularization is that the pseudoinverse defines a hard transition from
``on'' to ``off''. Modes are either set to zero or included in the map at their full amplitude. On
the other hand Tikhonov regularization smoothly interpolates between these behaviors. Because of
this, Tikhonov regularization tends to produce better results in practical applications.

In the event that the observer has a prior map of the sky, $\|\b a - \b a_\text{prior}\|^2$ can be
used as the regularizing norm. This will use the prior map to fill-in missing information instead of
setting these modes to zero. In this case the minimum is at
\begin{equation}
    \b{\hat a}_\text{with prior} = (\b B^*\b B + \varepsilon\b I)^{-1}
        (\b B^*(\b v - \b B\b a_\text{prior}))
        + \b a_\text{prior}\,.
\end{equation}
If instead the observer has a prior expectation on the covariance of the spherical harmonic
coefficients, Wiener filtering can also be used.  This technique is demonstrated for simulated
measurements by \citet{2016arXiv161203255B}.

Alternatively we could opt to regularize the problem by enforcing smoothness in the sky maps. In
this case, the regularizing norm should be of the form $\|\nabla I(\hat r)\|^2$, where $\nabla I$ is
the gradient of the sky brightness in the direction $\hat r$. This is actually a generalization of
Tikhonov regularization where the objective function is $\|\b v-\b B\b a\|^2 + \varepsilon\|\b A\b
a\|^2$ for some matrix $\b A$. The minimum is at
\begin{equation}
    \b{\hat a}_\text{generalized} = (\b B^*\b B + \varepsilon\b A^*\b A)^{-1}\b B^*\b v\,.
\end{equation}

Finally in many machine learning applications the $L_1$-norm\footnote{
    $\|\b a\|_1 = \sum_i |a_i|$
} is used in place of the usual $L_2$-norm in order to encourage sparsity in the reconstructed
signal. Applying this to $m$-mode analysis imaging would amount to minimizing $\|\b v-\b B\b a\|_2^2
+ \varepsilon\|\b a\|_1$. However, because we have decomposed the sky in terms of spherical
harmonics, the vector $\b a$ is not expected to be sparse. Consequently the $L_1$-norm is generally
inappropriate for $m$-mode analysis imaging without an additional change-of-variables designed to
introduce sparsity.

@@

We measure the flux of several bright sources (Cyg~A, Cas~A, Tau~A, Vir~A, Her~A, Hya~A,
Per~B\footnote{
    At 74~MHz, Per~B is about two times brighter than Per~A.
}, and
3C~353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, and $Z_8^8$) and the beam amplitude
at zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
model at several frequencies. This process is repeated for each frequency channel. Residuals for
Cyg~A and Cas~A can be seen in Figure~\ref{fig:scintillation}.

@@

Small scale fluctuations are best characterized by source scintillation and refractive offsets.
Figure~\ref{fig:scintillation} shows the apparent flux and position offset of Cyg~A and Cas~A as a
function of time over the entire observing period. Both sources exhibit rapid scintillation on the
timescale of a single integration (13 seconds). For example at 36.528 MHz, it is not unusual for Cyg
A to have measured flux variations of 50\% between adjacent 13 second integrations.  The variance at
36.528~MHz compared with the variance at 73.152~MHz is consistent with an ionospheric $\nu^{-2}$
origin. The measured position offset of each source is a measurement of the ionospheric phase
gradient across the array.  This varies on slower 10 minute timescales refracting each source by as
much as 20 arcmin (at 36.528 MHz) from their true astronomical positions as waves in the ionosphere
pass through the line of sight. At 74~MHz on the VLA, \citet{2007ApJS..172..686K} observe $\sim
1$~arcmin refractive offsets during the night, and $\sim 4$~arcmin offsets during the day on similar
$\sim10$ minute timescales.  The impact of these effects on the sky maps is simulated in
\S\ref{sec:ionosphere}.

@@

In order to account for propagation effects through the ionosphere, direction-dependent calibration
and peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S} must be used.  Direction-dependent
calibration allows the per-antenna amplitude and phase towards a bright astronomical source to be
free parameters. In the dataset used in this paper, scintillation and refractive-offset events on
the timescale of a single integration (13 seconds) are observed (Figure~\ref{fig:scintillation}).
Therefore the direction dependent calibration changes on these timescales and we must solve for one
set of complex gains per source per integration.

@@

Other bright sources -- namely Vir~A, Tau~A, Her~A, Hya~A, Per~B, and 3C~353 -- are also removed
from the visibilities prior to imaging. Because these sources are much fainter than Cyg~A and Cas~A,
we do not need resolved source models to be able to remove these sources from the visibilities
without residual sidelobes contaminating the image.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/spectral-index/ovro-lwa-sky-map.pdf}
    \caption{
        This Mollweide-projected map is constructed from 3 maps of the sky at 36.528~MHz (red),
        52.224~MHz (green), and 73.152~MHz (blue). The maps are scaled by $\nu^{2.5}$ before
        combining and the color scale is logarithmic (as in Figure~\ref{fig:channel-maps}).
        Therefore regions with a spectral index of $-2.5$ will tend to appear white. Areas with a
        steeper index appear red and areas with a flatter spectral index appear blue.
    }
    \label{fig:three-color}
\end{figure*}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/spectral-index/better-internal-spectral-index}
    \caption{
        The local spectral index measured between the 36.528~MHz map and the 73.152~MHz map
        estimated by means of a local T-T plot. The color scale gives the spectral index where blue
        is flat spectrum and red is steep spectrum. The contours give the
        coefficient-of-determination ($R^2$) for the linear fit to the local T-T plot. If $R^2$ is
        low, the quality of the fit is low and the estimated spectral index is unreliable. This can
        be either due to insufficient dynamic range in the local T-T plot or due to multiple
        emission mechanisms operating in close proximity. Consequently $R^2$ tends to drop at higher
        galactic latitudes (due to dynamic range), and near \ion{H}{2} regions in the galactic
        plane (due to multiple emission mechanisms).
    }
    \label{fig:internal-spectral-index}
\end{figure*}

\begin{figure*}[t]
    \centering
    \includegraphics[height=0.32\textheight]{figures/haslam/better-haslam-spectral-index}
    \caption{
        The local spectral index measured between the 73.152~MHz OVRO-LWA map and the reprocessed
        408~MHz Haslam map \citep{2015MNRAS.451.4311R}.  The color scale gives the spectral index
        where blue is flat spectrum and red is steep spectrum. The contours give the
        coefficient-of-determination ($R^2$) for the linear fit to the local T-T plot. See the
        caption of Figure~\ref{fig:internal-spectral-index} for more details about the
        coefficient-of-determination..
    }
    \label{fig:haslam-spectral-index}
\end{figure*}

@@

Each map from Figure~\ref{fig:channel-maps} will be made freely available online in Healpix format
\citep{2005ApJ...622..759G} on LAMBDA (\url{https://lambda.gsfc.nasa.gov/}).

Due to the considerations presented by \citet{2016ApJ...826..116V} and discussed in
\S\ref{sec:mmode-analysis}, each of these maps is monopole subtracted ($a_{00}=0$).  Furthermore, in
order to suppress sources of terrestrial interference, all spherical harmonics with $m=0$, or $m=1$
and $l>100$ are filtered from the map (where the spherical harmonics are defined in the J2017
coordinate system). As will be discussed in \S\ref{sec:rfi}, these spherical harmonics are
particularly susceptible to contamination by RFI and common-mode pickup. As a consequence,
astronomical emission that circles the J2017 north celestial pole (NCP) is filtered from the maps.
This filtering creates negative rings around the NCP at the declination of bright point sources, but
These rings are naturally removed from the map during CLEANing as long as this filtering step is
included in the PSF calculation.

The noise in each map is empirically measured using jackknife resampling. The dataset is split into
even- and odd-numbered integrations. These two groups are imaged and cleaned independently, before
being compared against the maps constructed from all of the available data using the standard
jackknife variance estimator. This estimate of the variance includes all sources of error that
operate on $\sim13$ second timescales (the integration time) such as thermal noise and rapid
ionospheric fluctuations, but does not account for more slowly varying effects (for example,
sidereal variation in the system temperature or day-night fluctuations in the ionosphere). These
noise calculations are summarized in Table~\ref{tab:summary}.  VLSSr source counts
\citep{2014MNRAS.440..327L} suggest that the confusion limit at 74 MHz and 15 arcmin angular
resolution is $\sim 1000\times(\nu/74\,{\rm MHz})^{-0.7}$ mJy.  Each channel map achieves thermal
noise $<900$ mJy and therefore each map is likely at or near the confusion limit.

In the absence of a zero-level correction, a pixel-by-pixel power law fit to the new maps is
impossible. In general this zero-level correction requires calibrated total power measurements that
will be included in future work.  Instead, temperature-temperature plots (T-T plot) can be used to
measure the spectral index independently of any zero-level corrections \citep{1962MNRAS.124..297T}.
This method relies on the assumption that all pixels in a given region are described by the same
power law. In that case there exists a linear relationship between the brightness temperature at
frequency $\nu_1$ and frequency $\nu_2$. The slope of this best-fit line is a measure of the
spectral index between the two frequencies. T-T plots can fail to obtain a reliable measure of the
spectral index in two ways.  First, if there is not enough dynamic range in the emission region
there may be only a weak correlation between the brightness temperature at $\nu_1$ and $\nu_2$.
Second, if two emission mechanisms operate in close proximity (ie.  synchrotron and free-free) then
a single power-law interpretation of the emission in that region will be poor. Consequently spectral
indices estimated from T-T plots can require careful interpretation.

In Figure~\ref{fig:internal-spectral-index} the spectral index is locally estimated in each part of
the sky within a region $\sim10^\circ$ across by constructing local T-T plots between 36.528~MHz and
73.152~MHz. Contours of constant $R^2$ (the coefficient-of-determination) are overlaid. If $R^2\sim
1$, the spectral index is reliable because there is locally a strong linear correlation between
36.528~MHz and 73.152~MHz. However if $R^2\ll 1$, the spectral index calculation is unreliable.
$R^2$ tends to drop in cold patches of the sky where there is not enough dynamic range to find a
strong correlation between the two frequencies. $R^2$ also tends to drop in the vicinity of
\ion{H}{2} regions in the galactic plane due to multiple emission mechanisms violating the
assumption of a single spectral index. Therefore we should restrict our interpretation of
Figure~\ref{fig:internal-spectral-index} to the galactic plane and north galactic spur. In the
galactic plane, the synchrotron spectral index varies between $\sim-2.5$ and $-2.75$. In the
vicinity of \ion{H}{2} regions the spectral index flattens significantly.  These \ion{H}{2} regions
can be seen with higher resolution in Figure~\ref{fig:three-color}. Along the galactic plane,
especially towards the galactic center, \ion{H}{2} regions appear as blue shadows due to free-free
absorption.

In the literature the spectral index at low frequencies is commonly computed with respect to the
Haslam 408~MHz map \citep{1981A&A...100..209H, 1982A&AS...47....1H}, which was reprocessed by
\citet{2015MNRAS.451.4311R} to remove artifacts associated with $1/f$ noise and bright sources.
Figure~\ref{fig:haslam-spectral-index} displays the spectral index computed between the 73.152~MHz
map and the reprocessed Haslam map. The spectral index was estimated by degrading the 73.152~MHz map
to the resolution of the Haslam map and constructing local T-T plots in every direction. The
coefficient-of-determination is overlaid as a contour plot, however because
$\log(408\,\text{MHz}/73.152\,\text{MHz}) > \log(73.152\,\text{MHz}/36.528\,\text{MHz})$, the
spectral indices presented in Figure~\ref{fig:haslam-spectral-index} tend to be more robust than
those presented in Figure~\ref{fig:internal-spectral-index}. This is reflected by the fact that
$R^2$ is larger, but the interpretation must still generally be restricted to the galactic plane.

\subsection{Comparisons with Other Sky Maps}\label{sec:compare}

\subsubsection{LWA1 Low Frequency Sky Survey}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/lwa1/lwa1}
    \caption{\todo{a thing}}
    \label{fig:lwa1-comparison}
\end{figure*}

The LWA1 Low Frequency Sky Survey (LLFSS) \citep{2017MNRAS.469.4537D} produced 9 maps of the sky
between 35~MHz and 80~MHz. 6 of these maps are interior to the frequency range spanned by this work.
A direct comparison with these LLFSS maps can be seen in Figure~\ref{fig:lwa1-comparison}. In this
figure the LLFSS maps are filtered to remove the monopole and all modes with $m=0$, and the OVRO-LWA
maps are interpolated in frequency and blurred to match the angular resolution of the corresponding
LWA1 map. The dominant feature in this map is a shift of the galactic plane. This feature is also
seen in comparisons of the LLFSS with the GSM (see for example Figure~9 of
\citet{2017MNRAS.469.4537D}). Therefore we conclude that this is an artifact of the LLFSS. Otherwise
at 60~MHz the agreement is generally better than 10\%. However at lower frequencies the agreement
deterioriates to about 20\%.

The LLFSS incorporates calibrated total power radiometry to estimate the missing flux from short
spacings. As a result \citet{2017MNRAS.469.4537D} report per-pixel spectral-indices from combining
all 9 sky maps. Care must be taken in comparing these spectral indices with
Figure~\ref{fig:internal-spectral-index} because they are susceptible to different systematic
errors. Both calculations are sensitive to mistakes in the antenna primary beam, but the LLFSS
spectral indices are additionally sensitive to errors in the zero-level. We will restrict the
comparison to the galactic plane where the spectral indices are likely to be the most reliable.
Towards the galactic center both surveys agree that the spectral index is very flat $>-2.2$ due to
the influence of free-free absorption.  However at galactic latitudes $\sim 180^\circ$ this work
suggests that the spectral index varies between -2.5 and -2.75, while the LLFSS reports
substantially flatter indices in the range -2.3 to -2.2. In this region $0.7 < R^2 < 0.9$ so this
could be an artifact of the comparatively weak correlation between the brightness at 36.528~MHz and
73.152~MHz, which tends to bias the spectral index towards $-\infty$.

The LLFSS also computes spectral indices with respect to the Haslam 408~MHz map. These spectral
indices are subject to the same caveats and systematic errors as before. However in general the
qualitative agreement with Figure~\ref{fig:haslam-spectral-index} is better potentially due to the
increased robustness associated with estimating spectral indices with a larger fractional bandwidth.

\subsubsection{Guzm\'{a}n 45 MHz Map}

The Guzm\'{a}n 45 MHz map \citep{2011A&A...525A.138G} is compiled from a southern hemisphere survey
\citep{1997A&AS..124..315A} and a northern hemisphere survey \citep{1999A&AS..140..145M} with a
small gap around the NCP. In this work the zero-level is set by comparing against published
low-frequency measurements in the literature in six different directions.

A direct comparison between the OVRO-LWA maps interpolated to 45 MHz and the Guzm\'{a}n 45 MHz map
can be seen in Figure~\ref{fig:guzman-comparison}. In order to make this comparison the OVRO-LWA map
was degraded to a 5$^\circ$ resolution by convolving with a Gaussian kernel, and the Guzm\'{a}n map
has had spherical harmonics with $m=0$ discarded in order to make it consistent with the maps
presented in this paper. This figure shows a $\sim20\%$ excess of emission in the galactic plane
that is consistent with the discrepancy observed between the LLFSS and the Guzm\'{a}n map.  However
while the LLFSS has an excess of emission near the north galactic pole, no such excess is observed
in this work. Instead there is a 10\% excess of emission near the south galactic pole. Elsewhere off
the plane of the galaxy the discrepancy can be as much as $-20\%$.

\citet{2011A&A...525A.138G} compute the spectral index between their 45~MHz map and the 408~MHz
Haslam map. Along the galactic plane the spectral index varies between -2.2 (in the vicinity of
\ion{H}{2} regions), and -2.5 (at galactic longitudes $\sim 180^\circ$). The north galactic spur has
a spectral index of -2.5. This is generally consistent with the results presented in
Figure~\ref{fig:haslam-spectral-index}.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/postage-stamps/3C134}
    \caption{
        A zoom-in of 3C~134 at 36.528~MHz (left panel), 52.224~MHz (middle panel), and 73.152~MHz
        (right panel). At 36.528~MHz there are $\sim10\%$ artifacts around 3C~134 that persist after
        CLEANing due to ionospheric effects. As expected for an ionospheric origin, these artifacts
        decrease in amplitude as frequency increases. Figure~\ref{fig:ionospheric-simulations} shows
        the typically expected amplitude of these effects for ionospheric scintillation and
        refractive offsets.
    }
    \label{fig:3C134}
\end{figure*}

The maps presented in Figure~\ref{fig:channel-maps} do not account for any off-diagonal terms
arising from ionospheric fluctuations. The effect of this can be seen in
Figure~\ref{fig:ionospheric-simulations}. In this simulation at 36.528~MHz, a point source is placed
at the location of Cas A. In the first panel the source flux traces the beam model exactly and the
source is always located exactly at the location of Cas A. In the middle panel, the source is
allowed to scintillate in the same way Cas A does in Figure~\ref{fig:scintillation}. The image of
the point source is effectively unchanged from the ideal PSF. In the right panel, the source
position is allowed to vary in the same way Cas A does in Figure~\ref{fig:scintillation}. The
refractive offsets lead to a clear degradation of the sidelobes. Because the sidelobes are altered
from that of the ideal PSF, refractive offsets will restrict the dynamic range it is possible to
obtain with the CLEAN algorithm described in \S\ref{sec:clean}. This effect can be clearly seen in
Figure~\ref{fig:3C134}, where 10\% errors within 1$^\circ$ of 3C~134 are seen at 36.528~MHz.  As
expected for an ionospheric effect these errors decrease to a few percent at 52.224~MHz, and less at
73.152~MHz. We therefore conclude that ionospheric effects directly limit the dynamic range in the
vicinity of bright point sources.

The second case is more subtle. Sources are observed at a wide range of locations in the primary
beam of the antenna. The imaging process must reconcile all of these observations together, and the
beam model provides the instructions for how to do this. In the event of an error in the beam model,
it can be expected that the beam will introduce errors into the sky maps that will limit the dynamic
range in the vicinity of bright point sources.  \citet{2015PhRvD..91h3514S} simulate the effect of
beam errors on a cosmological analysis concluding that the beam must be known to one part in $10^4$.
Our requirements are significantly less stringent because we are estimating the sky brightness
instead of estimating the amplitude of a faint cosmological signal in the presence of foreground
emission that dominates the signal by 5 orders of magnitude. In fact in \S\ref{sec:ionosphere} we
found that ionospheric effects likely dominate over other sources of error that affect the PSF
shape. Therefore we conclude that the beam models generated in \S\ref{sec:beam} are sufficient to
limit the effect of beam errors on the PSF to at least less than those introduced by the ionosphere.

@@
